Appendix to "Models for spatial structure in small-area estimation

### 2022-07-13 src/docs_paper/appendix.Rmd
Work on manuscript and simulation study

1. \textit{Scaling}
The structure matrix $\mathbf{R}$ should be rescaled to have generalised variance, defined by the geometric mean of the diagonal elements of its generalised inverse
\begin{equation}
    \sigma^2_{\text{GV}}(\mathbf{R}) = \prod_{i = 1}^n (R^-_{ii})^{1/n} = \exp \left( \frac{1}{n} \sum_{i = 1}^n \log (R^-_{ii}) \right),
\end{equation}
equal to one, by replacing $\mathbf{R}$ with $\mathbf{R}^\star = \mathbf{R} / \sigma^2_{\text{GV}}(\mathbf{R})$.
As the diagonal elements $R^-_{ii}$ correspond to marginal variances, the generalised variance gives a measure of the average marginal variance.
However, this measure, introduced by @sorbye2014scaling, ignores off-diagonal entries and more broadly any measure of typical variance could be used.
Scaling mitigates the influence of the adjacency graph on the variance of $\bphi$.
Allowing the variance to be controlled by $\tau_\phi$ alone is important as it allows for consistent, interpretable prior selection.
When the adjacency graph is disconnected it is not appropriate to scale the structure matrix $\mathbf{R}$ uniformly since for a given precision $\tau_\phi$, local smoothing operates on each connected component independently.
As such, each connected component should be scaled independently to have generalised variance one giving $\mathbf{R}^\star_I = \mathbf{R}_I / \sigma^2_{\text{GV}}(\mathbf{R}_I)$ where $\mathbf{R}_I$ is the sub-matrix of the structure matrix corresponding to index set $I$.

@@

>>>>

1. \textit{Scaling}
The structure matrix $R$ should be rescaled to have generalised variance, defined by the geometric mean of the diagonal elements of its generalised inverse
\begin{equation}
    \sigma^2_{\text{GV}}(R) = \prod_{i = 1}^n (R^-_{ii})^{1/n} = \exp \left( \frac{1}{n} \sum_{i = 1}^n \log (R^-_{ii}) \right),
\end{equation}
equal to one, by replacing $R$ with $R^\star = R / \sigma^2_{\text{GV}}(R)$.
As the diagonal elements $R^-_{ii}$ correspond to marginal variances, the generalised variance gives a measure of the average marginal variance.
However, this measure, introduced by @sorbye2014scaling, ignores off-diagonal entries and more broadly any measure of typical variance could be used.
Scaling mitigates the influence of the adjacency graph on the variance of $\bphi$.
Allowing the variance to be controlled by $\tau_\phi$ alone is important as it allows for consistent, interpretable prior selection.
When the adjacency graph is disconnected it is not appropriate to scale the structure matrix $R$ uniformly since for a given precision $\tau_\phi$, local smoothing operates on each connected component independently.
As such, each connected component should be scaled independently to have generalised variance one giving $R^\star_I = R_I / \sigma^2_{\text{GV}}(R_I)$ where $R_I$ is the sub-matrix of the structure matrix corresponding to index set $I$.

@@

\clearpage

# Simulation study

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=1]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-1}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=2]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-2}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=3]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-3}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=4]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-4}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=5]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-5}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=6]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-6}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=7]{depends/crps-boxplot-rho.pdf}}
\label{fig:crps-boxplot-rho-7}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=1]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-1}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=2]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-2}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=3]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-3}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=4]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-4}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=5]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-5}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=6]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-6}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=7]{depends/histogram-ecdf.pdf}}
\label{fig:histogram-ecdf-7}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=1]{depends/crps-maps.pdf}}
\label{fig:crps-maps-1}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=2]{depends/crps-maps.pdf}}
\label{fig:crps-maps-2}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=3]{depends/crps-maps.pdf}}
\label{fig:crps-maps-3}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=4]{depends/crps-maps.pdf}}
\label{fig:crps-maps-4}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=5]{depends/crps-maps.pdf}}
\label{fig:crps-maps-5}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=6]{depends/crps-maps.pdf}}
\label{fig:crps-maps-6}
\end{figure}

\begin{figure}[h]
\centering
\makebox[\textwidth][c]{\includegraphics[page=7]{depends/crps-maps.pdf}}
\label{fig:crps-maps-7}
\end{figure}

\clearpage

# HIV study

\clearpage
